Response to the defense feedback

### 2021-06-14 Chapter-4/Chapter-4.tex
Updates from Overleaf

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
uint8_t key[2], t1, t2;
get_key(key);              // 0 <= key[0], key[1] < 256
t1 = key[0] + key[1];
t2 = key[0] - key[1];
if (t1 < 4){               // leakage site A
    foo();    
}                          
if (t2 > 0){               // leakage site B     
    doo();    
}                          
\end{lstlisting}
    \vspace*{-1pt}
    \caption{Side-channel leakage}
    \label{fig:side-channel}
\end{figure}
In this chapter, we assume an attacker can observe the secret-dependent control-flows in Figure~\ref{fig:side-channel}.
Therefore, an attacker can have two different observations for each leak site
depending on the value of the $\mathit{key}$: $A$ for function \textsf{foo} is executed,
$\neg A$ for function \textsf{foo} is not executed, $B$ for function \textsf{doo} is
executed, and $\neg B$ for function \textsf{doo} is not executed. Now the
question is how much information can be leaked from the above code if an
attacker knows which branch is executed?

\begin{table}[ht]
    \centering\small\footnotesize
    \caption{The distribution of observation}\label{shtable}
    %    \resizebox{\columnwidth}{!}{
    \begin{tabular}{l|cc|cc}
        \hline

@@

\textbf{Shannon Entropy.}
Based on Shannon entropy, the respective amount of information in A and B equals to
    {\footnotesize
        \begin{align*}
            \mathit{Shannon\text{-}entropy_A} & = -(0.9998*\log_{2}0.9998      \\
                                              & \qquad+ 0.0002*\log_{2}0.0002) \\
                                              & = 0.000\ \mathrm{bits}         \\
            \mathit{Shannon\text{-}entropy_B} & = -(0.5*\log_{2}0.5            \\
                                              & \qquad+ 0.5*\log_{2}0.5)       \\
                                              & = 1.000\ \mathrm{bits}
        \end{align*}
    }
In the next section, we will show that these measures work well only
theoretically in a static analysis setting.
Generally, they do not apply to dynamic analysis or real
settings. We will present that the static or theoretical results could be
dramatically different from the real world, and we do need a better method to
quantify the information leakage from a practical point of view.

@@

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
char key[9] = input();
if(strcmp(key, "password"))   // leakage site C
    pass();                   // branch 1
else
    fail();                   // branch 2
\end{lstlisting}
    \vspace*{-10pt}
    \caption{A dummy password checker}
    \label{fig:password-checker}
\end{figure}

@@

\begin{table}[ht]
    \centering\small\footnotesize
    \caption{New leakage modeling results}
    \label{shtable2}
    \vspace*{-9pt}
    %    \resizebox{\columnwidth}{!}{
    \begin{tabular}{l|cc|cc}
        \hline

@@

\begin{figure}%[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
int mbedtls_internal_aes_encrypt( mbedtls_aes_context *ctx,
const unsigned char input[16],
unsigned char output[16] )
{
uint32_t *RK, X0, X1, X2, X3, Y0, Y1, Y2, Y3;
...
for( i = ( ctx->nr >> 1 ) - 1; i > 0; i-- )
{
    AES_FROUND( Y0, Y1, Y2, Y3, X0, X1, X2, X3 );   // Leakage 1
    AES_FROUND( X0, X1, X2, X3, Y0, Y1, Y2, Y3 );   // Leakage 2
}
AES_FROUND( Y0, Y1, Y2, Y3, X0, X1, X2, X3 );       // Leakage 3
X0 = *RK++ ^ \                                      // Leakage 4
    ( (uint32_t) FSb[ ( Y0       ) & 0xFF ]       ) ^
    ( (uint32_t) FSb[ ( Y1 >>  8 ) & 0xFF ] <<  8 ) ^
    ( (uint32_t) FSb[ ( Y2 >> 16 ) & 0xFF ] << 16 ) ^
    ( (uint32_t) FSb[ ( Y3 >> 24 ) & 0xFF ] << 24 );
// X1, X2, X3 do the same computation as X0
...                                                 // Leakage 5,6,7
PUT_UINT32_LE( X0, output,  0 );
...
return( 0 );
}
\end{lstlisting}
    \caption{Function \textit{mbedtls\_internal\_aes\_encrypt}}
    \label{mbedtls_aes}
\end{figure}

@@

\begin{figure*}
    \centering
    \vspace*{-9pt}
    \hspace*{-15pt}
    \subfloat[OpenSSL 0.9.7]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-0-9-7.pdf}
        \label{fig:rsa-1}
    }
    \subfloat[OpenSSL 1.0.2f]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-0-2f.pdf}
        \label{fig:rsa-2}
    }
    \subfloat[OpenSSL 1.0.2k]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-0-2k.pdf}
        \label{fig:rsa-3}
    }
        \hfill

@@

For vulnerabilities that leak less amount of information,
developers are more reluctant to fix them or fixing them unintentionally. For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace original function \textsf{BN\_mod\_exp\_mont}.
\tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \textbf{m}. In the updated version, developers make the fixed windows the default option and rewrite most of the function. However, the leakage site still exists in OpenSSL 1.1.1.
\begin{figure}
    \centering
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
# define mul_add_c2(a,b,c0,c1,c2)                    \
    t=(BN_ULLONG)a*b;                                \
    tt=(t+t)&BN_MASK;                                \
    if (tt < t) c2++;                                \
    t1=(BN_ULONG)Lw(tt);                             \
    t2=(BN_ULONG)Hw(tt);                             \
    c0=(c0+t1)&BN_MASK2;                             \
    if ((c0 < t1) && (((++t2)&BN_MASK2) == 0)) c2++; \
    c1=(c1+t2)&BN_MASK2; if ((c1) < t2) c2++;
\end{lstlisting}
    \vspace*{-6pt}
    \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 0.9.7}
    \label{fig:old_sqr2}
    \vspace*{-8pt}
\end{figure}

\begin{figure}
    \centering
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
# define mul_add_c2(a,b,c0,c1,c2)      do { \
    BN_ULONG ta = (a), tb = (b);            \
    BN_ULONG lo, hi, tt;                    \
    BN_UMULT_LOHI(lo,hi,ta,tb);             \
    c0 += lo; tt = hi+((c0<lo)?1:0);        \
    c1 += tt; c2 += (c1<tt)?1:0;            \
    c0 += lo; hi += (c0<lo)?1:0;            \
    c1 += hi; c2 += (c1<hi)?1:0;            \
    } while(0)
\end{lstlisting}
\caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 1.1.1}
\label{fig:new_sqr2}
\end{figure}

To evaluate the effectiveness of the leaked bits reported by \tool{}, we conduct a case study of all the leaked sites identidied by \tool{} in OpenSSL 1.1.0f. Table~\ref{chapter4:tab:RSAOpenSSL1.1.0} shows the result. First, all leakage sites that leak more than 5 bits information are fixed by developers. Second, for all leakages that are not patched by developers, the quantification result shows that they leak less than 1.0 bits information. The evaluation results show that \tool{} can help developers find severe leakages automatically.

\begin{table}[!ht]
\centering\tiny\scriptsize
\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0f. According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages. $0.0$ means very small amount of leakage, but not exactly zero.}\label{chapter4:tab:RSAOpenSSL1.1.0}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{rrrrc}
\hline
\textbf{File}  & \textbf{Line Number} & \textbf{Vulnerable Function} & \textbf{Leaked Information (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
bn\_lib.c& 143&BN\_num\_bits\_word&*& \cmark\\
bn\_lib.c& 144&BN\_num\_bits\_word&*& \cmark\\
bn\_lib.c& 145&BN\_num\_bits\_word&17.2 & \cmark\\
bn\_lib.c& 1029&bn\_correct\_top&*&\cmark\\
bn\_lib.c& 639&BN\_ucmp&*&\cmark\\
ct\_b64.c& 164&\_\_udivdi3&5.9 &\cmark\\
bn\_div.c& 330&BN\_div&*&\cmark\\
bn\_gcd.c& 192&int\_bn\_mod\_inverse&1.0 &\xmark\\
bn\_gcd.c& 215&int\_bn\_mod\_inverse&7.9 &\cmark\\
bn\_gcd.c& 237&int\_bn\_mod\_inverse&8.2 &\cmark\\
bn\_gcd.c& 218&int\_bn\_mod\_inverse&14.9 &\cmark\\
bn\_gcd.c& 240&int\_bn\_mod\_inverse&9.2 &\cmark\\
bn\_lib.c& 147&BN\_num\_bits\_word&*&\cmark\\
bn\_lib.c& 152&BN\_num\_bits\_word&12.6 &\cmark\\
bn\_lib.c& 153&BN\_num\_bits\_word&*&\cmark\\
bn\_lib.c& 156&BN\_num\_bits\_word&*&\cmark\\
bn\_div.c& 384&BN\_div&17.2 &\cmark\\
bn\_div.c& 330&BN\_div&11.9 &\cmark\\
bn\_div.c& 334&BN\_div&3.8 &\cmark\\
bn\_exp.c& 622&BN\_mod\_exp\_mont\_consttime&1.0 &\xmark\\
bn\_exp.c& 741&BN\_mod\_exp\_mont\_consttime&1.0 &\xmark\\
bn\_mont.c& 138&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 139&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 140&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 142&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 152&BN\_from\_montgomery\_word&*&\cmark\\
bn\_asm.c& 733&bn\_sqr\_comba8&*&\cmark\\
bn\_asm.c& 592&bn\_mul\_comba8&*&\cmark\\
bn\_mont.c& 98&BN\_from\_montgomery\_word&0.0 &\xmark\\
bn\_div.c& 330&BN\_div&0.3 &\xmark\\
bn\_div.c& 330&BN\_div&0.3 &\cmark\\
\hline
\end{tabular}
\end{table}

@@

Since the table look-ups and conditional jumps are replaced with single-bit logical gates, with no secret-dependent memory addresses or control flow, both the data access and control flow types of side-channel leakages are mitigated.
\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t password = input();

@@

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t password = input();

@@

\subsubsection*{Lookup Table}
\begin{figure}[h]
\centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
static const uint8_t T[1024] = {
      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U,
...
output = (T[(key[0]>>24)] << 24) ^
         (T[(key[1]>>16) & 0xff] << 16) ^
         (T[(key[2]>>8) & 0xff] << 8) ^
         (T[(key[3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup tables with small entries.}\label{fig:chapter4:small_lookup}
\end{figure}

\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
static const uint32_t T[256] = {
    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
...
output = (T[(key[0]>>24)] << 24) ^
         (T[(key[1]>>16) & 0xff] << 16) ^
         (T[(key[2]>>8) & 0xff] << 8) ^
         (T[(key[3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup tables with big entries.}\label{fig:chapter4:big_lookup}
\end{figure}

@@

\subsubsection*{Password Checker}
\begin{figure}
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  for (int i = 0; i < 2; ++i) {
    if (key[i] != pub[i]) {
      return false;
    }
  }
  return true;
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  bool matched = true;
  for (int i = 0; i < 2; ++i) {
    if (pub[i] != key[i]) 
      matched = false;
  }
  return matched;
}
\end{lstlisting}
  \end{minipage}
  \caption{A password checker. The left version is vulnerable to side-channel attacks. The right version is the fixed version.}\label{fig:chapter4:pwcheck}
\end{figure}

We illustrate the quantification method on a password checking example.  As shown in Figure~\ref{fig:chapter4:pwcheck}, the left version is vulnerable to side-channel attacks because of the early return at line 4. If the first bytes of \textsf{key} and \textsf{pub} are the same, the function will continue running and access the second byte. The right version fixes the vulnerability because the function will continue comparing the second byte even if the first byte is different.  \tool{} identifies the leakage site in the left figure successfully and estimates the amount of leakage is $16$ bits.

>>>>

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
uint8_t key[2], t1, t2;
get_key(key);              // 0 <= key[0], key[1] < 256
t1 = key[0] + key[1];
t2 = key[0] - key[1];
if (t1 < 4){               // leakage site A
    foo();    
}                          
if (t2 > 0){               // leakage site B     
    doo();    
}                          
\end{lstlisting}
    \vspace*{-1pt}
    \caption{Side-channel leakage}
    \label{fig:side-channel}
\end{figure}
In this chapter, we assume an attacker can observe the secret-dependent control-flows in Figure~\ref{fig:side-channel}.
Therefore, an attacker can have two different observations for each leak site
depending on the value of the $\mathit{key}$: $A$ for function \textsf{foo} is executed,
$\neg A$ for function \textsf{foo} is not executed, $B$ for function \textsf{doo} is
executed, and $\neg B$ for function \textsf{doo} is not executed. Now the
question is how much information can be leaked from the above code if an
attacker knows which branch is executed?

\begin{table}[ht]
    \centering%\small\footnotesize
    \caption{The distribution of observation}\label{shtable}
    %    \resizebox{\columnwidth}{!}{
    \begin{tabular}{l|cc|cc}
        \hline

@@

\textbf{Shannon Entropy.}
Based on Shannon entropy, the respective amount of information in A and B equals to
    {%\footnotesize
        \begin{align*}
            \mathit{Shannon\text{-}entropy_A} & = -(0.9998*\log_{2}0.9998      \\
                                              & \qquad+ 0.0002*\log_{2}0.0002) \\
                                              & = 0.000\ \mathrm{bits}         \\
            \mathit{Shannon\text{-}entropy_B} & = -(0.5*\log_{2}0.5            \\
                                              & \qquad+ 0.5*\log_{2}0.5)       \\
                                              & = 1.000\ \mathrm{bits}
        \end{align*}
    }
In the next section, we will show that these measures work well only
theoretically in a static analysis setting.
Generally, they do not apply to dynamic analysis or real
settings. We will present that the static or theoretical results could be
dramatically different from the real world, and we do need a better method to
quantify the information leakage from a practical point of view.

@@

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
char key[9] = input();
if(strcmp(key, "password"))   // leakage site C
    pass();                   // branch 1
else
    fail();                   // branch 2
\end{lstlisting}
    \vspace*{-10pt}
    \caption{A dummy password checker}
    \label{fig:password-checker}
\end{figure}

@@

\begin{table}[ht]
    \centering%\small\footnotesize
    \caption{New leakage modeling results}
    \label{shtable2}
    \vspace*{-9pt}
    %    \resizebox{\columnwidth}{!}{
    \begin{tabular}{l|cc|cc}
        \hline

@@

\begin{figure}%[h!]
    \centering
    \begin{lstlisting}[ frame=none]
int mbedtls_internal_aes_encrypt( mbedtls_aes_context *ctx,
const unsigned char input[16],
unsigned char output[16] )
{
uint32_t *RK, X0, X1, X2, X3, Y0, Y1, Y2, Y3;
...
for( i = ( ctx->nr >> 1 ) - 1; i > 0; i-- )
{
    AES_FROUND( Y0, Y1, Y2, Y3, X0, X1, X2, X3 );   // Leakage 1
    AES_FROUND( X0, X1, X2, X3, Y0, Y1, Y2, Y3 );   // Leakage 2
}
AES_FROUND( Y0, Y1, Y2, Y3, X0, X1, X2, X3 );       // Leakage 3
X0 = *RK++ ^ \                                      // Leakage 4
    ( (uint32_t) FSb[ ( Y0       ) & 0xFF ]       ) ^
    ( (uint32_t) FSb[ ( Y1 >>  8 ) & 0xFF ] <<  8 ) ^
    ( (uint32_t) FSb[ ( Y2 >> 16 ) & 0xFF ] << 16 ) ^
    ( (uint32_t) FSb[ ( Y3 >> 24 ) & 0xFF ] << 24 );
// X1, X2, X3 do the same computation as X0
...                                                 // Leakage 5,6,7
PUT_UINT32_LE( X0, output,  0 );
...
return( 0 );
}
\end{lstlisting}
    \caption{Function \textit{mbedtls\_internal\_aes\_encrypt}}
    \label{mbedtls_aes}
\end{figure}

@@

\begin{figure*}
    \centering
    %\vspace*{-9pt}
    %\hspace*{-15pt}
    \subfloat[OpenSSL 0.9.7]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-0-9-7.pdf}
        \label{fig:rsa-1}
    }
    \subfloat[OpenSSL 1.0.2f]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-0-2f.pdf}
        \label{fig:rsa-2}
    }
    \subfloat[OpenSSL 1.0.2k]{
        \includegraphics[width=.3\linewidth]{./figures/chapter4/result/RSA-openssl-1-0-2k.pdf}
        \label{fig:rsa-3}
    }
        \hfill

@@

For vulnerabilities that leak less amount of information,
developers are more reluctant to fix them or fixing them unintentionally. For example, OpenSSL 0.9.7 adds a fixed windows version of function \textsf{BN\_mod\_exp\_mont\_consttime} to replace original function \textsf{BN\_mod\_exp\_mont}.
\tool{} detects a minor vulnerability in the original function that can leak the last bit of the big number \textbf{m}. In the updated version, developers make the fixed windows the default option and rewrite most of the function. However, the leakage site still exists in OpenSSL 1.1.1.
\begin{figure}
    \centering
    \begin{lstlisting}[xleftmargin=.08\textwidth, xrightmargin=.0\textwidth, frame=none]
# define mul_add_c2(a,b,c0,c1,c2)                    \
    t=(BN_ULLONG)a*b;                                \
    tt=(t+t)&BN_MASK;                                \
    if (tt < t) c2++;                                \
    t1=(BN_ULONG)Lw(tt);                             \
    t2=(BN_ULONG)Hw(tt);                             \
    c0=(c0+t1)&BN_MASK2;                             \
    if ((c0 < t1) && (((++t2)&BN_MASK2) == 0)) c2++; \
    c1=(c1+t2)&BN_MASK2; if ((c1) < t2) c2++;
\end{lstlisting}
    \vspace*{-6pt}
    \caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 0.9.7}
    \label{fig:old_sqr2}
    \vspace*{-8pt}
\end{figure}

\begin{figure}
    \centering
    \begin{lstlisting}[xleftmargin=.08\textwidth, xrightmargin=.0\textwidth, frame=none]
# define mul_add_c2(a,b,c0,c1,c2)      do { \
    BN_ULONG ta = (a), tb = (b);            \
    BN_ULONG lo, hi, tt;                    \
    BN_UMULT_LOHI(lo,hi,ta,tb);             \
    c0 += lo; tt = hi+((c0<lo)?1:0);        \
    c1 += tt; c2 += (c1<tt)?1:0;            \
    c0 += lo; hi += (c0<lo)?1:0;            \
    c1 += hi; c2 += (c1<hi)?1:0;            \
    } while(0)
\end{lstlisting}
\caption{Macro \textsf{sqr\_add\_c2} in OpenSSL 1.1.1}
\label{fig:new_sqr2}
\end{figure}

To evaluate the effectiveness of the leaked bits reported by \tool{}, we conduct a case study of all the leaked sites identified by \tool{} in OpenSSL 1.1.0f. Table~\ref{chapter4:tab:RSAOpenSSL1.1.0} shows the result. First, all leakage sites that leak more than 5 bits information are fixed by developers. Second, for all leakages that are not patched by developers, the quantification result shows that they leak less than 1.0 bits information. The evaluation results show that \tool{} can help developers find severe leakages automatically.

\begin{table}[!ht]
\centering\tiny\scriptsize
\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0f. According to \tool{}\cite{bao2021abacus}, the mark ``$*$'' means timeout, which indicates more severe leakages. $0.0$ means very small amount of leakage, but not exactly zero.}\label{chapter4:tab:RSAOpenSSL1.1.0}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{lrrrc}
\hline
\textbf{File}  & \textbf{Line Number} & \textbf{Vulnerable Function} & \textbf{Leaked Information (bits)} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
bn\_lib.c& 143&BN\_num\_bits\_word&*& \cmark\\
bn\_lib.c& 144&BN\_num\_bits\_word&*& \cmark\\
bn\_lib.c& 145&BN\_num\_bits\_word&17.2 & \cmark\\
bn\_lib.c& 1029&bn\_correct\_top&*&\cmark\\
bn\_lib.c& 639&BN\_ucmp&*&\cmark\\
ct\_b64.c& 164&\_\_udivdi3&5.9 &\cmark\\
bn\_div.c& 330&BN\_div&*&\cmark\\
bn\_gcd.c& 192&int\_bn\_mod\_inverse&1.0 &\xmark\\
bn\_gcd.c& 215&int\_bn\_mod\_inverse&7.9 &\cmark\\
bn\_gcd.c& 237&int\_bn\_mod\_inverse&8.2 &\cmark\\
bn\_gcd.c& 218&int\_bn\_mod\_inverse&14.9 &\cmark\\
bn\_gcd.c& 240&int\_bn\_mod\_inverse&9.2 &\cmark\\
bn\_lib.c& 147&BN\_num\_bits\_word&*&\cmark\\
bn\_lib.c& 152&BN\_num\_bits\_word&12.6 &\cmark\\
bn\_lib.c& 153&BN\_num\_bits\_word&*&\cmark\\
bn\_lib.c& 156&BN\_num\_bits\_word&*&\cmark\\
bn\_div.c& 384&BN\_div&17.2 &\cmark\\
bn\_div.c& 330&BN\_div&11.9 &\cmark\\
bn\_div.c& 334&BN\_div&3.8 &\cmark\\
bn\_exp.c& 622&BN\_mod\_exp\_mont\_consttime&1.0 &\xmark\\
bn\_exp.c& 741&BN\_mod\_exp\_mont\_consttime&1.0 &\xmark\\
bn\_mont.c& 138&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 139&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 140&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 142&BN\_from\_montgomery\_word&*&\cmark\\
bn\_mont.c& 152&BN\_from\_montgomery\_word&*&\cmark\\
bn\_asm.c& 733&bn\_sqr\_comba8&*&\cmark\\
bn\_asm.c& 592&bn\_mul\_comba8&*&\cmark\\
bn\_mont.c& 98&BN\_from\_montgomery\_word&0.0 &\xmark\\
bn\_div.c& 330&BN\_div&0.3 &\xmark\\
bn\_div.c& 330&BN\_div&0.3 &\cmark\\
\hline
\end{tabular}
\end{table}

@@

Since the table look-ups and conditional jumps are replaced with single-bit logical gates, with no secret-dependent memory addresses or control flow, both the data access and control flow types of side-channel leakages are mitigated.
\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t password = input();

@@

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t password = input();

@@

\subsubsection*{Lookup Table}
\begin{figure}[h]
\centering
    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.05\textwidth, frame=none]
static const uint8_t T[1024] = {
      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U,
...
output = (T[(key[0]>>24)] << 24) ^
         (T[(key[1]>>16) & 0xff] << 16) ^
         (T[(key[2]>>8) & 0xff] << 8) ^
         (T[(key[3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup tables with small entries.}\label{fig:chapter4:small_lookup}
\end{figure}

\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.05\textwidth, xrightmargin=.05\textwidth, frame=none]
static const uint32_t T[256] = {
    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
...
output = (T[(key[0]>>24)] << 24) ^
         (T[(key[1]>>16) & 0xff] << 16) ^
         (T[(key[2]>>8) & 0xff] << 8) ^
         (T[(key[3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup tables with big entries.}\label{fig:chapter4:big_lookup}
\end{figure}

@@

\subsubsection*{Password Checker}
\begin{figure}
  \begin{minipage}{0.8\linewidth}
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  for (int i = 0; i < 2; ++i) {
    if (key[i] != pub[i]) {
      return false;
    }
  }
  return true;
}
\end{lstlisting}\caption{A vulnerable password checker.}\label{fig:chapter4:pwcheck1}
  \end{minipage}
  \vfill
  \begin{minipage}{0.8\linewidth}
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.00\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  bool matched = true;
  for (int i = 0; i < 2; ++i) {
    if (pub[i] != key[i]) 
      matched = false;
  }
  return matched;
}
\end{lstlisting}\caption{A safe password checker.}\label{fig:chapter4:pwcheck2}
\end{minipage}
\end{figure}

We illustrate the quantification method on two password checking examples.  As shown in Figure~\ref{fig:chapter4:pwcheck1}, the version is vulnerable to side-channel attacks because of the early return at line 4. If the first bytes of \textsf{key} and \textsf{pub} are the same, the function will continue running and access the second byte. Figure~\ref{fig:chapter4:pwcheck2} fixes the vulnerability because the function will continue comparing the second byte even if the first byte is different.  \tool{} identifies the leakage site in Figure~\ref{fig:chapter4:pwcheck1} successfully, and estimates the amount of leakage is $16$ bits.
